Cognitive Principles and Individual Differences \\ in Human Syllogistic Reasoning

### 2019-11-07 paper/paper-v3.tex
rewrote intro

Even though the main logical formalism of Classical Logic (CL) has successfully been applied to our scientific reasoning,
various experimental studies have shown that human reasoning systematically deviates 
from conclusions valid under CL (cf.~\cite{wason:68,byrne:89}). Originally, one of the objectives of using (non-classical) logic in the field of AI and logic programming was to formalize human reasoning and commonsense reasoning~\cite{McCarthy59,McCarthy98}. 
% However, the proposed approaches did not have the expected successes~(cf.~\cite{mcdermott:87}),
% as they were mostly theoretical and did not apply to real case studies.
On the other hand, cognitive scientists have extensively investigated and acquired a great expertise human thinking.
However, only recently an attempt was made to bridge the gap among these disciplines.
% this expertise was not consulted, i.e. there was no communication among the relevant fields.

@@

Another aspect that would be intersting to investigate is in how far the $\cxt$ operator within the extended three-valued {\L}ukasiewicz logic,
originally presented in~\cite{}, 
 corresponds to the {\L}ukasiewicz extensional necessity operator~\cite{}.\footnote{Thanks to the reviewer for this observation.}

>>>>

Even though the main logical formalism of Classical Logic (CL) has successfully been applied to our scientific reasoning,
various experimental studies have shown that human reasoning systematically deviates 
from conclusions valid under CL (cf.~\cite{wason:68,byrne:89}).
Originally, one of the objectives in the field of AI and logic programming was to formalize human reasoning and commonsense reasoning~\cite{McCarthy59,McCarthy98}. 
However, the proposed approaches have been strongly critized~(cf.~\cite{mcdermott:87}).
On the other hand, cognitive scientists have extensively investigated and acquired a great expertise
in human thinking. Recently, several attempts have been made to bridge the gap among these disciplines. 
% as they were mostly theoretical and did not apply to real case studies.
% However, only recently an attempt was made 
% this expertise was not consulted, i.e. there was no communication among the relevant fields.

@@

Another aspect that would be intersting to investigate is in how far the semantics of the $\cxt$ operator within the extended three-valued {\L}ukasiewicz logic in Section~\ref{sub:3valuedL}, 
 corresponds to the {\L}ukasiewicz extensional necessity operator~\cite{}.\footnote{Thanks to the
 anonymous reviewer for this observation.}
